---
title: Build, Deploy and Communicate with R Packages
author:
  - name: Ben Barnard
    affiliation: Team Member Insights, Wells Fargo
    address:
    - 
    email: ben.j.barnard@wellsfargo.com
  - name: Gabriel Odom
    affiliation: Department of Biostatistics, Florida Internatinal University Stempel College of Public Health
    address:
    - Miami, FL 33199, USA
    email:  godom@fiu.edu
  - name: Layla Bouzoubaa
    affiliation: Sylvester Comprehensive Cancer Center, University of Miami Miller School of Medicine
    address:
      - Miami, FL, 33136, USA
    email: lab218@miami.edu
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

## Introduction

Introductory section which may include references in parentheses
[@R], or cite a reference such as @R in the text.

## Section title in sentence case

This section may contain a figure such as Figure \ref{fig:Rlogo}.

```{r, Rlogo, echo=FALSE, fig.cap='The logo of R.', out.width='2in', fig.align='center', fig.pos='htbp'}
knitr::include_graphics('Rlogo.pdf')
```

## Another section

There will likely be several sections, perhaps including code snippets, such as:

```{r}
x <- 1:10
x
```

## Summary

This file is only a basic article template. For full details of _The R Journal_ style and information on how to prepare your article for submission, see the [Instructions for Authors](https://journal.r-project.org/share/author-guide.pdf).

\bibliography{RJreferences}
